---
title: "virus 2"
output: html_document
date: '2022-06-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
newdata<- read.csv(file="clinicalTrial.csv")
```

```{r eval=FALSE}
newdata <- newdata %>%
mutate(across(where(is.character), as.factor))
```

###Graphical results:

```{r}
barchartGC(~ infected+vaxStatus ,data=newdata)
barchartGC(~infected+ vaxStatus,data=newdata, type="percent")

```

It seems that the people who weren't affected by covid and took the vaccines have the same percentage. Out of the people who got affected: the highest numbers wee for those who didn't take the vaccine, then comes just taking the first , after that it's just taking the new vaccine, and the best situation with the least number of people infected is taking both the first and new vaccine.

###Numerical results:
```{r}
table1 <- xtabs(~infected + vaxStatus, data=newdata)
rowPerc(table1)
colPerc(table1)
```

The first row in the first table represents the first graph, and it shows that the number of people not infected for each category of vaccination is almost the same. the second row represents the second graph, where we see that the highest number of people infected is from the unvaccinated group , and then first, then new , and the one with the least infections is first and new.
and then the second table shows the percentage of people who got infected and didn't get infected in each category of vaccination.and it shows that the first+new group has the least percentage of infection, while the none group has the highest percentage of infection.


###Inferential results:
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1 ,simulate.p.value=TRUE)
```

the p value is very low so we can't see that there is a significant difference.
We run a fisher test.


```{r}
fisherXY = function(x, y, confL = 0, printAll=FALSE){
  # Inputs: 
  #   x: factor variable, 2 levels
  #   y: factor variable, n levels
  # confL: confidence level, default = 0.95
  #        print only those tables, results if p-value < (1-confL)
  # printAll: overide the 'print only if p-value < (1-confL), and
  #           print all tables and fisher test results
  #
  # Constraint:
  #   x and y must be same length
  #
  # Outputs:
  #   All 2x2 Fisher exact tests
  
  if(confL<0 || confL> 1){
    print('error: confL must be between 0 and 1')
    return(999)
  }
  
  if(!is.factor(x)) x=as.factor(x)
  if(!is.factor(y)) y=as.factor(y)
  
  fisherTable = as.matrix(table(x, y))
  cat('\ncontingency table:\n')
  print(fisherTable)
  cat('\n***All 2X2 tests****\n\n')

  # all 2x2 tests
  levelsY = levels(y)
  levelsX = levels(x)
  
  m = length(levelsX)
  n = length(levelsY)
  
  confLevel = 0.95
  if (confL !=0 ) confLevel=confL
  
  for (i in 1:(m-1))
       for(j in ((i+1):m))
          for (k in 1:(n-1))
             for (l in ((k+1):n)) {
                
                 fisherIndexX = c(i,j)
                 fisherIndexY = c(k,l)
                 
                 fTempTable = as.matrix(fisherTable[fisherIndexX,
                                        fisherIndexY])
                 
                 fisherTest=fisher.test(fTempTable, conf.int = TRUE, 
                              conf.level = confLevel)
                 
                 if((fisherTest$p.value < (1-confLevel) ) || printAll){
                   
                       print(c(levelsX[i], levelsX[j]))
                       print(c(levelsY[k], levelsY[l]))
                       print(fTempTable)
                       print(fisherTest)
                       cat('\n')
                 }
                 
        }
}

```
```{r}
fisherXY(newdata$vaxStatus,newdata$infected)
```

First with first+new: the p value is less than 0.05 so there is a significant different. meaning that there is a reason why taking the first+new vaccines is better than just taking the first.

The p value for first and new is lower than 0.05 but it's not as low as first with first+new , showing that the difference between first and first+new is bigger meaning that first+new is the best then new then first.
 and using the same concept for comparison for the other tests we can see that first+new is the most effective , then new, then first.
 
 
 
 
